%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \large#3 & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Vinayak Thakur } \\ \vspace{1pt}
     Bengaluru, India \\ \vspace{1pt}
    \small  \raisebox{-0.1\height}\faPhone\ \underline{+91-9462988266} ~ \raisebox{-0.2\height}\faEnvelope\  \underline{vinayak9thakur@gmail.com} ~ 
    \href{https://www.linkedin.com/in/vinayakthakur17/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{https://www.linkedin.com/in/vinayakthakur17/}}  ~
    \vspace{-4pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CMR Institute of Technology, Bengaluru }{ 2021 -- 2025}
      {Bachelor of Engineering in Computer Science Engineering, CGPA: 8.48}{Bengaluru, India}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Emmanuel Mission School , Bundi }{2012 -- 2020}
      {Grade: Class X = 91.4\% , Class XII = 91.4\% }{Bundi, India}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{COURSES / CURRICULUM }
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Data Structures \&Algorithms
                \item Operating System
                \item DBMS
                \item Computer Networks
                \item OOPS
                \item Version Control
                \item Web Design

            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

     \resumeSubheading{Fidrox Technologies\href{https://bizsense.in/}{\raisebox{-0.1\height} } }{Oct 2024 -- Jan 2025}{\underline{Intern}}{Bengaluru}
      \resumeItemListStart
        \resumeItem{\normalsize{
Designed and developed UI dashboards and screens for various access management systems using HTML, CSS, JavaScript, and AdminLTE, ensuring a responsive and user-friendly interface.

 }}
   \resumeItem{\normalsize{
 Integrated UI components and interactive elements utilizing Bootstrap, jQuery, Toastr, and jqGrid, enhancing user experience and system accessibility.
}}
\resumeItem{\normalsize{
 Collaborated on UI/UX design improvements, leveraging Figma for prototyping and wireframing, streamlining the design-to-development workflow for seamless implementation.


 }}
   
      \resumeItemListEnd  
      \vspace{-1pt}
    
       \resumeSubheading{Centre of Excellence(ML), CMR Institute 
\href{https://weboin.com/}{\raisebox{-0.1\height} } }{Oct 2022 -- Nov 2022}{\underline{Intern}}{Bengaluru}
      \resumeItemListStart
        \resumeItem{\normalsize{
Explored the fundamentals of Machine Learning and Big Data, gaining hands-on experience with Python, Pandas, Matplotlib, and Seaborn for data analysis and visualization.

 }}
   \resumeItem{\normalsize{
Worked on link prediction using the NetworkX library, implementing ML techniques to analyze network structures and predict relationships between nodes.
}}
  
\resumeItem{\normalsize{
Applied clustering algorithms like K-Means and statistical analysis techniques to real-world datasets, documenting findings through detailed report-making and data-driven insights.
}}
      \resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {{\textbf{\large{Virtual Try-On Using Deep Learning}} \href{Project Link}{\raisebox{-0.1\height} }}}{Dec 2024}
        \resumeItemListStart
    \resumeItem{\normalsize{Developed a deep learning-based virtual try-on system that transfers clothing onto human models using GMM (Geometric Matching Module) and U-Net-based generators.}}
    \resumeItem{\normalsize{Utilized pose estimation and TPS warping for accurate cloth alignment, improving try-on quality over existing methods.}}
    \resumeItem{\normalsize{Trained and fine-tuned models on the VITON dataset, optimizing performance for high-resolution virtual clothing synthesis.}}
\resumeItemListEnd

          
      \resumeProjectHeading
          {{\textbf{\large{Customer Relationship Management}} \href{Project Link}{\raisebox{-0.1\height} }} }{July 2024}
          \resumeItemListStart
    \resumeItem{\normalsize{Developed a CRM system to streamline customer data management, assessments, and billing for a cybersecurity company, improving workflow efficiency.}}
    \resumeItem{\normalsize{Built using Django, SQLite, HTML, CSS, and Bootstrap, ensuring a responsive UI and seamless user experience.}}
    \resumeItem{\normalsize{Integrated secure authentication and role-based access control, enhancing data protection and user privacy.}}
\resumeItemListEnd

          
          \resumeProjectHeading
      {\href{https://}{\textbf{\large{Ration Shop Management System}} \href{https://}{\raisebox{-0.1\height} }} }{Dec 2023}
        \resumeItemListStart
    \resumeItem{\normalsize{Developed a user-friendly inventory and stock control system for ration shops using HTML, CSS, JavaScript, Bootstrap, PHP, and MySQL.}}
    \resumeItem{\normalsize{Implemented real-time stock tracking and automated inventory updates, improving efficiency in ration distribution.}}
    \resumeItem{\normalsize{Designed a responsive and intuitive UI, enhancing user experience and accessibility across devices.}}
\resumeItemListEnd

          
    \resumeSubHeadingListEnd
\vspace{-15pt}

%



%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.01in, label={}]
    \item \small{
    \begin{tabular}{@{}ll}
     \textbf{\normalsize{Languages (Programming):}}{{\textbf{}C++, C, Java, Python, SQL, HTML, CSS, JavaScript } \\
     
     \textbf{\normalsize{Frameworks:}} {React, Django, Express, Bootstrap } \\
     \textbf{\normalsize{Operating Systems:}} {Linux, Windows, MacOS} \\
    \textbf{\normalsize{Tools and Technologies::}} {Git, GitHub, VsCode, NodeJs, Xampp, IntelliJ Idea, Visual Studio Code, MySQL, Figma} \\
     \textbf{\normalsize{Languages:}} {English, Hindi, German} \\
    \end{tabular}
    }
 \end{itemize}


 \vspace{-18pt}
  %-----------CERTIFICATIONS---------------

%-----------INVOLVEMENT---------------
\section{POSITIONS OF RESPONSIBILITY}
\vspace{-1pt}

\noindent \hangindent=1.2cm $\sbullet[.75]$ \textbf{Event Coordinator - Cultura CMRIT}: Organised multiple cultural events at the annual cultural fest. \\

\noindent \hangindent=0.289cm $\sbullet[.75]$ \textbf{Member - TAB Theatre Club}: Secured First Prize in street play competition at BMSCE, showcasing creative expression and teamwork abilities. \\

\noindent \hangindent=0.289cm $\sbullet[.75]$ \textbf{Campus Leadership}: Elected as Class Representative for two consecutive terms during undergraduate studies, demonstrating leadership and accountability. \\

\noindent \hangindent=1.2cm $\sbullet[.75]$ Facilitated promotion of institute's incubation center through strategic information drives and diverse outreach initiatives. \\



\vspace{-5pt}

            



 \end{document}
